---
title: "Summary"
author: "X"
date: "03/14/2026"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r}
#remotes::install_version("readxlsb", version = "0.1.61")
```

```{r}
#install.packages("zoo")
```

```{r}
#BiocManager::install("sva", ask = FALSE, update = FALSE)
```

```{r}
#install.packages("readxlsb")
```

```{r}
library(readr)
library(dplyr)
library(BiocManager)
library(pamr)
library(preprocessCore)
library(glmnet)
library(randomForest)
library(e1071)
library(HiDimDA)
library(ipred)
library(vsn)
library(MGSDA)
library(xgboost)
library(umap)
library(data.table)
library(Matrix)
library(lightgbm)
library(limma)
library(reshape)
library(ggplot2)
library(grid)
library(caret)
library(readxl)
library(sva)
library(EDASeq)
library(edgeR)
library(RUVSeq)
library(Biobase)
library(BiocGenerics)
library(tidyverse)
library(readxlsb)
library(ranger)
library(zoo)
```

#the necessary parameters raw_data: data numeric dataframe(row-features/ column-samples) log2_transform: is the dataset need lo2 transform: T or F class_id: class of each samples factor vector(row-sample/ column-class)

#batch_id: batch id of each samples vector if there isn't batch information, use umap to classify different batches

#normlization function non-RNASeq:QN, MED, VSN RNASeq: TMM, TC, UQ, MED, DESeq, PoissonSeq, QN

#nonRNASeq: QN、MED、VSN；

#RNASeq: TMM、TC、UQ、MED、DESeq、PoissionSeq、QN

```{r frozne_qn}
quant.norm<-function(data = NULL,train = NULL, test = NULL, ref.dis = NULL){
  train <- as.matrix(data[, train, drop = FALSE])
  test  <- as.matrix(data[, test,  drop = FALSE])
  if(!is.null(train) && !is.null(test)) stopifnot(nrow(train) == nrow(test))
  if(is.null(train)) stopifnot(!is.null(ref.dis))
  
  if(!is.null(train)){
    # quantile normalization training
    train.qn <- preprocessCore::normalize.quantiles(train, copy = TRUE)
    dimnames(train.qn) <- dimnames(train)
    
    ref.dis <- as.numeric(sort(train.qn[, 1]))
  } else train.qn <- NULL
  
  if(is.null(test)){
    test.fqn <- NULL
  } else{
    ## frozen quantile normalize test
    test.fqn <- apply(test, 2, function(x) {
      ord <- rank(x, ties.method = "first")
      ref.dis[ord]
      })
    test.fqn <- as.matrix(test.fqn)

    if (ncol(test) == 1) {
      test.fqn <- matrix(test.fqn, nrow = nrow(test), ncol = 1)
                         }
    rownames(test.fqn) <- rownames(test)
    colnames(test.fqn) <- colnames(test)

  }
  
  return(list("train.qn" = train.qn,
              "test.fqn" = test.fqn,
              "ref.dis" = ref.dis))
}
```

```{r med_norm}
"med.norm" <- function(data = NULL,train = NULL, test = NULL, ref.dis = NULL){
  train <- as.matrix(data[, train, drop = FALSE])
  test  <- as.matrix(data[, test,  drop = FALSE])
  if(!is.null(train) && !is.null(test)) stopifnot(nrow(train) == nrow(test))
  if(is.null(train)) stopifnot(!is.null(ref.dis))
  
  if(!is.null(train)){
    # median normalization training
    ref.dis <- median(train)
    temp <- apply(train, 2, median) - ref.dis
    shifts.train <- matrix(rep(temp, each = nrow(train)), ncol = ncol(train))
    train.mn <- train - shifts.train
  } else train.mn <- NULL
  
  if(is.null(test)) {
    test.fmn <- NULL
  } else{
    temp <- apply(test, 2, median) - ref.dis
    shifts.test <- matrix(rep(temp, each = nrow(test)), ncol = ncol(test))
    test.fmn <- test - shifts.test
  }
  
  return(list("train.mn" = train.mn,
              "test.fmn" = test.fmn,
              "ref.dis" = ref.dis))
}
```

```{r vs_norm}
"vs.norm" <- function(data = NULL,train = NULL, test = NULL, ref.dis = NULL){
  train <- as.matrix(data[, train, drop = FALSE])
  test  <- as.matrix(data[, test,  drop = FALSE])
  if(!is.null(train) && !is.null(test)) stopifnot(nrow(train) == nrow(test))
  if(is.null(train)) stopifnot(!is.null(ref.dis))
  
  if(!is.null(train)){
    # vsn training
    train0 <- 2^train #说明原数据是log2格式！
    ref.dis <- vsn::vsn2(train0)
    train.vsn <- log2(exp(as.matrix(ref.dis)))
  } else train.vsn <- NULL
  
  if(is.null(test)) {
    test.fvsn <- NULL
  } else {
    test0 <- 2^test
    test.fvsn0 <- vsn::vsn2(test0, ref.dis)
    test.fvsn <- log2(exp(as.matrix(test.fvsn0)))
  }
  
  return(list("train.vsn" = train.vsn,
              "test.fvsn" = test.fvsn,
              "ref.dis" = ref.dis))
}
```

```{r RNA_Seq_norm}
precision <- methods::setClass(
  "precision",
  slots = c(
    raw.train.data = "ANY",  ## for the clustering, we only consider the train data, it should be a list
    raw.test.data = "ANY",
    harmon.train.data = "list",
    harmon.test.data = "list",

    classification.result = "list",
    cluster.result = "list"
  )
)
create_precision.classification <- function(traindata, testdata, trainlabel, testlabel) {
  object <- methods::new(Class = "precision",
                         raw.train.data = list(data = traindata, label = trainlabel),
                         raw.test.data = list(data = testdata, label = testlabel)
                         )
  return(object)
}

harmon.method.TMM <- function(raw, groups) {
  dat.DGE <- DGEList(counts = raw,
                     group = factor(groups),
                     genes = rownames(raw))
  d <- calcNormFactors(dat.DGE, method = "TMM")
  scaling.factor <- d$samples$norm.factors * d$samples$lib.size / 1e6
  dat.harmonized <- cpm(d)
  res <- list(dat.harmonized = dat.harmonized, scaling.factor = scaling.factor)
  return(res)
}
harmon.TMM <- function(object){
  object@harmon.train.data$TMM <- harmon.method.TMM(raw = object@raw.train.data$data,
                                                    groups = object@raw.train.data$label)
  if(!is.null(object@raw.test.data)){
    object@harmon.test.data$TMM <- harmon.method.TMM(raw = object@raw.test.data$data,
                                                     groups = object@raw.test.data$label)
  }
  return(object)
}



harmon.method.TC <- function(raw, groups) {
  dat.DGE <- DGEList(counts = raw,
                     group = factor(groups),
                     genes = rownames(raw))
  scaling.factor <- dat.DGE$samples$lib.size/1e6
  dat.harmonized <- cpm(dat.DGE, normalized.lib.sizes = F)
  res <- list(dat.harmonized = dat.harmonized, scaling.factor = scaling.factor)
  return(res)
}
harmon.TC <- function(object){
  object@harmon.train.data$TC <- harmon.method.TC(raw = object@raw.train.data$data,
                                                  groups = object@raw.train.data$label)
  if(!is.null(object@raw.test.data)){
    object@harmon.test.data$TC <- harmon.method.TC(raw = object@raw.test.data$data,
                                                   groups = object@raw.test.data$label)
  }
  return(object)
}



harmon.method.UQ <- function(raw, groups) {
  dat.DGE <- DGEList(counts = raw,
                     group = factor(groups),
                     genes = rownames(raw))
  q.factor <- apply(dat.DGE$counts, 2, function(x) quantile(x[x != 0], probs = 0.75))
  scaling.factor <- q.factor/1e6
  dat.harmonized <- t(t(raw)/scaling.factor)
  res <- list(dat.harmonized = dat.harmonized, scaling.factor = scaling.factor)
  return(res)
}
harmon.UQ <- function(object){
  object@harmon.train.data$UQ <- harmon.method.UQ(raw = object@raw.train.data$data,
                                                  groups = object@raw.train.data$label)
  if(!is.null(object@raw.test.data)){
    object@harmon.test.data$UQ <- harmon.method.UQ(raw = object@raw.test.data$data,
                                                   groups = object@raw.test.data$label)
  }
  return(object)
}



harmon.method.med <- function(raw, groups) {
  dat.DGE <- DGEList(counts = raw,
                     group = factor(groups),
                     genes = rownames(raw))
  m.factor <- apply(dat.DGE$counts, 2, function(x) median(x[x != 0]))
  scaling.factor <- m.factor/1e6
  dat.harmonized <- t(t(raw)/scaling.factor)
  res <- list(dat.harmonized = dat.harmonized, scaling.factor = scaling.factor)
  return(res)
}
harmon.med <- function(object){
  object@harmon.train.data$med <- harmon.method.med(raw = object@raw.train.data$data,
                                                    groups = object@raw.train.data$label)
  if(!is.null(object@raw.test.data)){
    object@harmon.test.data$med <- harmon.method.med(raw = object@raw.test.data$data,
                                                     groups = object@raw.test.data$label)
  }
  return(object)
}


#data leakage
harmon.method.DESeq <- function(raw, groups) {
  colnames(raw) <- paste0("V", 1:(dim(raw)[2]))
  condition <- data.frame(SampleName = colnames(raw), Condition = factor(groups))
  rownames(condition) = colnames(raw)
  dat.DGE <- DESeq2::DESeqDataSetFromMatrix(countData = raw, colData = condition, design = ~ Condition)
  dat.DGE <- DESeq2::estimateSizeFactors(dat.DGE)
  scaling.factor <- DESeq2::sizeFactors(dat.DGE)
  dat.harmonized <- DESeq2::counts(dat.DGE, normalized = T)
  res <- list(dat.harmonized = dat.harmonized, scaling.factor = scaling.factor)
  return(res)
}
harmon.DESeq <- function(object){
  object@harmon.train.data$DESeq <- harmon.method.DESeq(raw = object@raw.train.data$data,
                                                        groups = object@raw.train.data$label)
  if(!is.null(object@raw.test.data)){
    object@harmon.test.data$DESeq <- harmon.method.DESeq(raw = object@raw.test.data$data,
                                                         groups = object@raw.test.data$label)
  }
  return(object)
}


harmon.method.PoissonSeq <- function(raw) {
  scaling.factor <- PoissonSeq::PS.Est.Depth(raw)
  dat.harmonized <- t(t(raw)/scaling.factor)
  res <- list(dat.harmonized = dat.harmonized, scaling.factor = scaling.factor)
  return(res)
}
harmon.PoissonSeq <- function(object){
  object@harmon.train.data$PoissonSeq <- harmon.method.PoissonSeq(raw = object@raw.train.data$data)
  if(!is.null(object@raw.test.data)){
    object@harmon.test.data$PoissonSeq <- harmon.method.PoissonSeq(raw = object@raw.test.data$data)
  }
  return(object)
}

harmon.method.QN <- function(raw){

  dat.harmonized <- preprocessCore::normalize.quantiles(as.matrix(raw))
  colnames(dat.harmonized) <- colnames(raw)
  rownames(dat.harmonized) <- rownames(raw)
  res <- list(dat.harmonized = dat.harmonized)
  return(res)
}

harmon.method.QN.frozen <- function(rawtrain,rawtest){

  dat.harmonized <- preprocessCore::normalize.quantiles(as.matrix(rawtrain))
  colnames(dat.harmonized) <- colnames(rawtrain)
  rownames(dat.harmonized) <- rownames(rawtrain)
  ref.dis <- as.numeric(sort(dat.harmonized[, 1]))
  dat.harmonized.test <- apply(rawtest, 2, function(x){ord <- rank(x); ref.dis[ord]})
  rownames(dat.harmonized.test) <- rownames(dat.harmonized)
  res <- list(dat.harmonized = dat.harmonized.test)
  return(res)
}

harmon.QN <- function(object){
  object@harmon.train.data$QN <- harmon.method.QN(raw = object@raw.train.data$data)
  if(!is.null(object@raw.test.data)){
    object@harmon.test.data$QN <- harmon.method.QN.frozen(rawtrain = object@raw.train.data$data,rawtest = object@raw.test.data$data)
  }
  return(object)
}
```

#ml function pam,svm,lasso,xgboost,knn,random forest

```{r ml_function}
#ml function

#pam
"pam.intcv" <- function(X, y, vt.k = NULL, n.k = 30, kfold = 5, folds = NULL, seed){
  
  ptm <- proc.time()
  set.seed(seed)
  data.pam  <- list(x = X, y = factor(y), geneids = rownames(X), genenames = rownames(X))
  fit.pam	<- pamr::pamr.train(data.pam, threshold=vt.k, n.threshold = n.k)
  fit.cv <-  new.pamr.cv(fit = fit.pam, data = data.pam, nfold = kfold)
  best.threshold <- fit.cv$threshold[max(which(fit.cv$error == min(fit.cv$error)))]
  
  mc <- fit.cv$error[which.min(fit.cv$error)]
  
  model <- pamr::pamr.train(data.pam, threshold = best.threshold, n.threshold = n.k)

## skip pamr.listgenes because it is unstable here and not used by ml_sum error calculation
  coefs <- NA

  time <- proc.time() - ptm
  return(list(mc = mc, time = time, model = model, cfs = coefs))
}
"new.pamr.cv" <- function (fit, data, nfold = 5, ...){
  x <- data$x[fit$gene.subset, fit$sample.subset, drop = FALSE]
  if (is.null(fit$newy)) {
    y <- factor(data$y[fit$sample.subset])
  }
  else {
    y <- factor(data$newy[fit$sample.subset])
  }
  this.call <- match.call()
  nsccv2 <- get("nsccv", envir = asNamespace("pamr"))
  balanced.folds <- get("balanced.folds", envir = asNamespace("pamr"))
  folds = balanced.folds(y, nfolds = nfold)
  junk <- nsccv2(x, y, object = fit, folds = folds,
                 survival.time = data$survival.time,
                 censoring.status = data$censoring.status,
                 ngroup.survival = fit$ngroup.survival,
                 problem.type = fit$problem.type,
                 ...) # changed here
  junk$call <- this.call
  junk$newy <- fit$newy
  junk$sample.subset <- fit$sample.subset
  return(junk)
}
"trycatch.func" <- function(expr, msg = "") {
  out <- tryCatch({
    expr
    
  }, warning = function(cond) {
    message("warning: ")
    message(cond)
    # Choose a return value in case of warning
    return(NULL)
    
  }, error = function(cond) {
    message("error: ")
    message(cond)
    # Choose a return value in case of error
    return(NA)
    
  }, finally={
    message(msg)
    
  })
  return(out)
}
"pam.predict" <- function(pam.intcv.model, pred.obj, pred.obj.group.id){
  pred <- pamr::pamr.predict(pam.intcv.model$model, newx = as.matrix(pred.obj),
  threshold = pam.intcv.model$model$threshold,
  type = "class")
  pred <- as.vector(pred)

  mc <- tabulate.ext.err.func(pred, pred.obj.group.id)
  prob <- pamr::pamr.predict(pam.intcv.model$model, newx = as.matrix(pred.obj),
                             threshold = pam.intcv.model$model$threshold,
                             type = "posterior")
  prob <- as.matrix(prob)
  return(list(pred=pred, mc=mc, prob=prob))
}

#svm
"svm.intcv" <- function(kfold = 5, X, y, seed){
  ptm <- proc.time()
  set.seed(seed)
  
  svm_tune = tune.svm(x = data.matrix((X)), y = factor(y), tunecontrol = tune.control(cross = kfold))
  
  time <- proc.time() - ptm
  return(list(mc = svm_tune$best.performance, time = time, model = svm_tune$best.model))
}

"svm.predict" <- function(svm.intcv.model, pred.obj, pred.obj.group.id){
  
  pred <- predict(svm.intcv.model$model, newdata = t(pred.obj))
  mc <- tabulate.ext.err.func(pred, pred.obj.group.id)
  
  return(list(pred=pred, mc=mc))
}
#lasso
lasso.intcv<-function(kfold = 5, X, y, seed, alp = 1){
  ptm <- proc.time()
  set.seed(seed)
  
  cv.fit <- glmnet::cv.glmnet(x = data.matrix(t(X)), y = factor(y),
                              family = "binomial", type.measure = "class", alpha = alp, nfold = kfold)
  mc <- cv.fit$cvm[which(cv.fit$lambda == cv.fit$lambda.1se)]
  #best.lambda <- cv.fit$lambda.1se # can be extracted from cv.fit
  coefs <- trycatch.func(coef(cv.fit, s = "lambda.1se"))
  time <- proc.time() - ptm
  return(list(mc=mc, time=time, model=cv.fit, cfs=coefs))
}
lasso.predict<-function(lasso.intcv.model, pred.obj, pred.obj.group.id){
  pred <- predict(lasso.intcv.model$model, newx = t(pred.obj),
                  s = lasso.intcv.model$model$lambda.1se,
                  type = "class")
  
  mc <- tabulate.ext.err.func(pred, pred.obj.group.id)
  prob <- predict(lasso.intcv.model$model, newx = t(pred.obj),
                  s = lasso.intcv.model$model$lambda.1se)
  return(list(pred=pred, mc=mc, prob=prob))
}

#xgboost
cvxgb <- function(datacv, fold) {
  minerror <- Inf
  
  for (min_child_weightvalue in seq(1, 9, 4)) {
    param <- list(
      min_child_weight = min_child_weightvalue,
      objective = "binary:logistic"
    )
    
    cvout <- xgb.cv(
      data = datacv,
      nrounds = 100,
      nfold = fold,
      params = param,
      metrics = list("error"),
      maximize = FALSE,
      verbose = FALSE,
      early_stopping_rounds = 20
    )
    
    eval_log <- cvout$evaluation_log
    test_col <- grep("^test.*error.*mean$", colnames(eval_log), value = TRUE)
    
    if (length(test_col) != 1) {
      stop("Cannot uniquely identify test error column in xgb.cv evaluation_log.")
    }
    
    test_err <- eval_log[[test_col]]
    
    if (min(test_err) < minerror) {
      minerror <- min(test_err)
      best_param <- param
      index <- which.min(test_err)
    }
  }
  
  return(list(param = best_param, nround = index, cverror = minerror))
}

"xgboost.intcv" <- function(kfold = 5, X, y, seed) {
  ptm <- proc.time()
  set.seed(seed)
  
  dtrain <- xgb.DMatrix(data = t(X), label = y)
  cvresult <- cvxgb(datacv = dtrain, fold = kfold)
  bestparam <- cvresult$param
  bestparam$eval_metric <- "error"
  
  print("best param is")
  print(bestparam)
  
  nround <- cvresult$nround
  
  trainresult <- xgb.train(
    data = dtrain,
    nrounds = nround,
    params = bestparam,
    verbose = 0
  )
  
  time <- proc.time() - ptm
  
  return(list(mc = cvresult$cverror, time = time, model = trainresult))
}

#knn
"knn.intcv" <- function(kfold = 5, X, y, seed){
  ptm <- proc.time()
  set.seed(seed)
  
  
  ctrl <- trainControl(method = "repeatedcv",
                       repeats = 3,
                       number = kfold)
  knn <- train(x = data.matrix(t(X)), y = factor(y),
               method = "knn",
               tuneLength = 9,
               trControl = ctrl)
  
  time <- proc.time() - ptm
  return(list(mc = 1 - max(knn$results$Accuracy), time = time, model = knn, cfs = NULL))
}

"knn.predict" <- function(knn.intcv.model, pred.obj, pred.obj.group.id){
  
  
  pred <- predict(knn.intcv.model$model, newdata = data.matrix(t(pred.obj)))
  mc <- tabulate.ext.err.func(pred, pred.obj.group.id)
  
  return(list(pred=pred, mc=mc))
}

#random forest
"ranfor.intcv" <- function(kfold = 5, X, y, seed){
  ptm <- proc.time()
  set.seed(seed)
  
  
  control <- trainControl(method='cv', 
                          number=5, 
                          search = 'random')
  
  rf <- train(x = data.matrix(t(X)), y = factor(y),
              method = 'ranger',
              metric = 'Accuracy',
              tuneLength = 5,
              preProcess = c("center", "scale"),
              trControl = control)
  
  

  time <- proc.time() - ptm
  return(list(mc = 1 - max(rf$results$Accuracy), time = time, model = rf, cfs = NULL))
}

"ranfor.predict" <- function(ranfor.intcv.model, pred.obj, pred.obj.group.id){
  
  pred <- predict(ranfor.intcv.model$model, newdata = t(pred.obj))
  mc <- tabulate.ext.err.func(pred, pred.obj.group.id)
  
  return(list(pred=pred, mc=mc))
}

"tabulate.ext.err.func" <- function(pred.obj, obs.grp){
  return(1 - sum(diag(table(pred.obj, obs.grp)))/length(obs.grp))
  }
```

# ml loop

```{r}
#n: times of ml
#data: log2 transformed dataframe (row:features, col:samples)
#class: a vector contain class id (factor 0 and 1)
#batch: a vector contain batch id
#batch_time: Whether to divide batches by time
#early_batch_id: if batch_time is not F, plug in the early batch id
#batch_balance: Should the two batches be trimmed to the same length
#ml: ml methods
#split_combination: a vector containing number meaning splitting strategy
#e.g.: c(50,70,80,90,100)
#data_type_rnaseq: whether the data is RNA-seq
#file: prefix of the result file name

#make sure that the colnames of data is the same as the names of batch
ml_sum <-  function (n = times,
                     data,
                     class,
                     batch,
                     batch_time = FALSE,
                     early_batch_id,
                     batch_balance = FALSE,
                     ml,
                     split_combination,
                     data_type_rnaseq = FALSE,
                     file) {
  #create a array to save results
  dim1 <- as.character(split_combination)
  if (data_type_rnaseq == TRUE) {
    dim2 = c("non", "TC", "UQ", "med", "TMM", "DESeq", "PoissonSeq", "QN")
  } else{
    dim2 <- c("non", "qn", "mn", "vsn")
  }
  dim3 = as.character(seq(1, n))
  for (ml_method in ml) {
    eval(parse(
      text = paste0(
        ml_method,
        "_result=array(NA,dim=c(length(dim1),length(dim2),length(dim3)),dimnames=list(dim1,dim2,dim3))"
      )
    ))
  }
  
  #Convert dataframe to vector
  class <- as.factor(as.vector(class))
  
  for (k in 1:n) {
    set.seed(k + 2024)
    unique_batch <- unique(batch)
    if (batch_time) {
      batch1 <- which(batch %in% early_batch_id)
      batch2 <- which(!batch %in% early_batch_id)
    } else {
      unique_chars <- unique(batch)
      shuffled_unique_chars <- sample(unique_chars)
      half_length <- ceiling(length(shuffled_unique_chars) / 2)
      group1_chars <- shuffled_unique_chars[1:half_length]
      group2_chars <-
        shuffled_unique_chars[(half_length + 1):length(shuffled_unique_chars)]
      batch1 <- which(batch %in% group1_chars)
      batch2 <- which(batch %in% group2_chars)
    }
    
    for (split in split_combination) {
      i = which(split == split_combination)
      
      #trim the two batches to the same length if batch_balance is T
      if (batch_balance == TRUE) {
        length_diff <- abs(length(batch1) - length(batch2))
        if (length(batch1) > length(batch2)) {
          batch1_id <- batch1[-sample(1:length(batch1), length_diff)]
          batch2_id <- batch2
        } else {
          batch1_id <- batch1
          batch2_id <- batch2[-sample(1:length(batch2), length_diff)]
        }
      } else {
        batch1_id <- batch1
        batch2_id <- batch2
      }
      
      #extract x% from batch1 and (100-x)% from batch2, merge them into train_id
      #and the rest will be test_id.
      n_train_2 <- floor(length(batch2_id) * (100 - split) / 100)
      n_train_1 <- floor(length(batch1_id) * split / 100)
      train_2 <- sample(batch2_id, n_train_2)
      train_1 <- sample(batch1_id, n_train_1)
      train_id <- sort(c(train_2, train_1))
      
      test_2 <- batch2_id[(!(batch2_id %in% train_2))]
      test_1 <- batch1_id[(!(batch1_id %in% train_1))]
      test_id <- sort(c(test_2, test_1))
      
      train_label <- class[train_id]
      test_label <- class[test_id]
      
      #Perform different normalization based on whether the dataset is RNA-seq
      if (data_type_rnaseq == TRUE) {
        object = create_precision.classification(traindata = data[, train_id],
                                                 testdata = data[, test_id],
                                                 train_label,
                                                 test_label)
        object <- harmon.TC(object)
        object <- harmon.UQ(object)
        object <- harmon.med(object)
        object <- harmon.TMM(object)
        object <- harmon.DESeq(object)
        object <- harmon.PoissonSeq(object)
        object <- harmon.QN(object)
      }
      
      for (norm in dim2) {
        if (data_type_rnaseq == TRUE) {
          j = which(norm == c(
            "non",
            "TC",
            "UQ",
            "med",
            "TMM",
            "DESeq",
            "PoissonSeq",
            "QN"
          ))
          if (norm == "non") {
            train <- object@raw.train.data$data
            test <- object@raw.test.data$data
          } else{
            eval(parse(
              text = paste0(
                "train <- object@harmon.train.data$",
                norm,
                "$dat.harmonized"
              )
            ))
            eval(parse(
              text = paste0(
                "test <- object@harmon.test.data$",
                norm,
                "$dat.harmonized"
              )
            ))
          }
          train_label <- object@raw.train.data$label
          test_label <- object@raw.test.data$label
        } else{
          if (norm == "non") {
            j = 1
            test = as.matrix(data[, test_id, drop = FALSE])
            train = as.matrix(data[, train_id, drop = FALSE])
          }
          if (norm == "qn") {
            j = 2
            qn_result = quant.norm(data, train_id, test_id)
            test = qn_result$test.fqn
            train = qn_result$train.qn
          }
          if (norm == "mn") {
            j = 3
            mn_result = med.norm(data, train_id, test_id)
            test = mn_result$test.fmn
            train = mn_result$train.mn
          }
          if (norm == "vsn") {
            j = 4
            vsn_result = vs.norm(data, train_id, test_id)
            test = vsn_result$test.fvsn
            train = vsn_result$train.vsn
          }
        }
        for (ml_method in ml) {
          cat(">>> k =", k,
          "| split =", split,
          "| norm =", norm,
          "| ml =", ml_method, "\n")
          flush.console()
          if (ml_method == "knn") {
            knn.intcv.model = knn.intcv(
              kfold = 5,
              X = (train),
              y = train_label,
              seed = k
            )
            pred.obj = (test)
            pred.obj.group.id = test_label
            pred <-
              predict(knn.intcv.model$model, newdata = data.matrix(t(pred.obj)))
            error = mean(pred != test_label)
          }
          if (ml_method == "lasso") {
            lasso.intcv.model = lasso.intcv(X = (train),
                                            y = train_label,
                                            seed = k)
            error = mean(
              predict(
                lasso.intcv.model$model,
                newx = t(test),
                s = lasso.intcv.model$model$lambda.1se,
                type = "class"
              ) != test_label
            )
            
          }
          if (ml_method == "pam") {
            pam.intcv.model = pam.intcv(
              kfold = 5,
              X = as.matrix(train),
              y = train_label,
              seed = k
            )
            pred_pam <- pamr.predict(
              pam.intcv.model$model,
              newx = as.matrix(test),
              threshold = pam.intcv.model$model$threshold,
              type = "class"
              )
            pred_pam <- as.vector(pred_pam)
            error = mean(pred_pam != as.vector(test_label))

          }
          if (ml_method == "rf") {
            ranfor.intcv.model = ranfor.intcv(
              kfold = 5,
              X = (train),
              y = train_label,
              seed = k
            )
            pred.obj = (test)
            pred.obj.group.id = test_label
            pred <-
              predict(ranfor.intcv.model$model, newdata = t(pred.obj))
            error = mean(pred != test_label)
          }
          if (ml_method == "svm") {
            svm.intcv.model = svm.intcv(
              kfold = 5,
              X = t(train),
              y = train_label,
              seed = k
            )
            pred.obj = (test)
            pred.obj.group.id = test_label
            error = mean(predict(svm.intcv.model$model, newdata = t(pred.obj)) !=
                           test_label)
          }
          if (ml_method == "xgb") {
            label_levels <- levels(train_label)
            xgboost.intcv.model = xgboost.intcv(
              X = train,
              y = as.numeric(train_label) - 1,
              seed = k
            )
            pred_prob <- predict(xgboost.intcv.model$model, t(test))
            pred_num  <- as.numeric(pred_prob > 0.5)

            pred_class <- factor(
              label_levels[pred_num + 1],
              levels = label_levels
            )
            test_label <- factor(test_label, levels = label_levels)

            error <- mean(pred_class != test_label)
          }
          eval(parse(text = paste0(
            ml_method, "_result[i,j,k]=error"
          )))
        }
      }
    }
  }
  for (ml_method in ml) {
    eval(parse(text = paste0("result<<-", ml_method, "_result")))
    filename = paste(file,
                     n,
                     ml_method,
                     "batch_balance",
                     batch_balance,
                     "result.csv",
                     sep = "_")
    write.table(
      result,
      file = filename,
      sep = "\t",
      col.names = NA,
      quote = FALSE
    )
  }
}

```

```{r result plot}
result_plot <- function(n,
                        ml,
                        file,
                        batch_balance=FALSE,
                        data_type_rnaseq=FALSE,
                        split_combination){
  error = vector("numeric")
  se = vector("numeric")
  for(i in ml){
    if(data_type_rnaseq == FALSE){
      norm <- c("None","QN","MN","VSN")
    filename <- paste(file,n,i,"batch_balance",batch_balance,"result.csv",sep="_")
    eval(parse(text = paste0(i,"_result=read.csv('",filename,"',sep='\t')")))
    eval(parse(text = paste0(i,"_result_non=rowMeans((",i,"_result[,-1,drop=FALSE])[,c(TRUE,FALSE,FALSE,FALSE),drop=FALSE])")))
    eval(parse(text = paste0(i,"_result_qn=rowMeans((",i,"_result[,-1,drop=FALSE])[,c(FALSE,TRUE,FALSE,FALSE),drop=FALSE])")))
    eval(parse(text = paste0(i,"_result_mn=rowMeans((",i,"_result[,-1,drop=FALSE])[,c(FALSE,FALSE,TRUE,FALSE),drop=FALSE])")))
    eval(parse(text = paste0(i,"_result_vsn=rowMeans((",i,"_result[,-1,drop=FALSE])[,c(FALSE,FALSE,FALSE,TRUE),drop=FALSE])")))

    eval(parse(text = paste0(i,"_result_non_se=apply((",i,"_result[,-1,drop=FALSE])[,c(TRUE,FALSE,FALSE,FALSE),drop=FALSE],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_qn_se=apply((",i,"_result[,-1,drop=FALSE])[,c(FALSE,TRUE,FALSE,FALSE),drop=FALSE],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_mn_se=apply((",i,"_result[,-1,drop=FALSE])[,c(FALSE,FALSE,TRUE,FALSE),drop=FALSE],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_vsn_se=apply((",i,"_result[,-1,drop=FALSE])[,c(FALSE,FALSE,FALSE,TRUE),drop=FALSE],1,sd)/sqrt(n)")))
    
    eval(parse(text = paste0("error = c(error,",i,"_result_non,",i,"_result_qn,",i,"_result_mn,",i,"_result_vsn)")))
    eval(parse(text = paste0("se = c(se,",i,"_result_non_se,",i,"_result_qn_se,",i,"_result_mn_se,",i,"_result_vsn_se)")))
    }else{
      norm <- c("non", "TC", "UQ", "med", "TMM", "DESeq", "PoissonSeq", "QN")
      filename <- paste(file,n,i,"batch_balance",batch_balance,"result.csv",sep="_")
    eval(parse(text = paste0(i,"_result=read.csv('",filename,"',sep='\t')")))
    eval(parse(text = paste0(i,"_result_non=rowMeans((",i,"_result[,-1])[,c(TRUE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_TC=rowMeans((",i,"_result[,-1])[,c(FALSE,TRUE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_UQ=rowMeans((",i,"_result[,-1])[,c(FALSE,FALSE,TRUE,FALSE,FALSE,FALSE,FALSE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_med=rowMeans((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,TRUE,FALSE,FALSE,FALSE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_TMM=rowMeans((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,FALSE,TRUE,FALSE,FALSE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_DESeq=rowMeans((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,FALSE,FALSE,TRUE,FALSE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_PoissonSeq=rowMeans((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,TRUE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_QN=rowMeans((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,TRUE)])")))
    
    eval(parse(text = paste0(i,"_result_non_se=apply((",i,"_result[,-1])[,c(TRUE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_TC_se=apply((",i,"_result[,-1])[,c(FALSE,TRUE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_UQ_se=apply((",i,"_result[,-1])[,c(FALSE,FALSE,TRUE,FALSE,FALSE,FALSE,FALSE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_med_se=apply((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,TRUE,FALSE,FALSE,FALSE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_TMM_se=apply((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,FALSE,TRUE,FALSE,FALSE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_DESeq_se=apply((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,FALSE,FALSE,TRUE,FALSE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_PoissonSeq_se=apply((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,TRUE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_QN_se=apply((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,FALSE,TRUE)],1,sd)/sqrt(n)")))
    
    eval(parse(text = paste0("error = c(error,",i,"_result_non,",i,"_result_TC,",i,"_result_UQ,",i,"_result_med,",i,"_result_TMM,",i,"_result_DESeq,",i,"_result_PoissonSeq,",i,"_result_QN)")))
    eval(parse(text = paste0("se = c(se,",i,"_result_non_se,",i,"_result_TC_se,",i,"_result_UQ_se,",i,"_result_med_se,",i,"_result_TMM_se,",i,"_result_DESeq_se,",i,"_result_PoissonSeq_se,",i,"_result_QN_se)")))
    }
  }
  strategy = factor(split_combination)
  result_result = data.frame(error = error,
                             se = se,
                             ml = rep(ml,each=length(norm)*length(split_combination)),
                             norm = rep(norm, each = length(split_combination), 
                                        times = length(ml)),
                             x=rep(1:length(split_combination),length(norm)*length(ml)))
  p=ggplot(result_result,aes(x=x,y=error,color=ml,linetype=norm))+
    geom_line()+
    scale_x_continuous(breaks=1:length(split_combination),labels=split_combination)+
    geom_errorbar(aes(ymin=error-se*1.96,ymax=error+se*1.96),width=0.1)+
    labs(x = "", title = paste0(toupper(substring(file, 1, 1)), substring(file, 2)))
  print(p)
}
```

```{r result plot triple splitting}
result_plot_all <- function(n,
                        ml,
                        file_contrast1,
                        file_contrast2,
                        batch_balance,
                        data_type_rnaseq,
                        split_comination){
  error = vector("numeric")
  se = vector("numeric")
  for(i in ml){
    filename=paste(file_contrast2,n,i,"batch_balance",batch_balance,"result.csv",sep="_")
    eval(parse(text = paste0(i,"_result=read.csv('",filename,"',sep='\t')")))
    eval(parse(text = paste0(i,"_result_non=rowMeans((",i,"_result[,-1])[,c(TRUE,FALSE,FALSE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_qn=rowMeans((",i,"_result[,-1])[,c(FALSE,TRUE,FALSE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_mn=rowMeans((",i,"_result[,-1])[,c(FALSE,FALSE,TRUE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_vsn=rowMeans((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,TRUE)])")))
    
    eval(parse(text = paste0(i,"_result_non_se=apply((",i,"_result[,-1])[,c(TRUE,FALSE,FALSE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_qn_se=apply((",i,"_result[,-1])[,c(FALSE,TRUE,FALSE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_mn_se=apply((",i,"_result[,-1])[,c(FALSE,FALSE,TRUE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_vsn_se=apply((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,TRUE)],1,sd)/sqrt(n)")))
    
    eval(parse(text = paste0("error = c(error,",i,"_result_non,",i,"_result_qn,",i,"_result_mn,",i,"_result_vsn)")))
    eval(parse(text = paste0("se = c(se,",i,"_result_non_se,",i,"_result_qn_se,",i,"_result_mn_se,",i,"_result_vsn_se)")))
  }
  result_1 = data.frame(error = error,
                             se = se,
                             ml = rep(ml,each=4*length(1)),
                             norm = rep(c("None","QN","MN","VSN"),each=length(1),length(ml)),
                             x=rep(length(split_comination)+1,4*length(ml)))
  
  error = vector("numeric")
  se = vector("numeric")
  for(i in ml){
    filename=paste(file_contrast1,n,i,"batch_balance",batch_balance,"result.csv",sep="_")
    eval(parse(text = paste0(i,"_result=read.csv('",filename,"',sep='\t')")))
    eval(parse(text = paste0(i,"_result_non=rowMeans((",i,"_result[,-1])[,c(TRUE,FALSE,FALSE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_qn=rowMeans((",i,"_result[,-1])[,c(FALSE,TRUE,FALSE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_mn=rowMeans((",i,"_result[,-1])[,c(FALSE,FALSE,TRUE,FALSE)])")))
    eval(parse(text = paste0(i,"_result_vsn=rowMeans((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,TRUE)])")))
    
    eval(parse(text = paste0(i,"_result_non_se=apply((",i,"_result[,-1])[,c(TRUE,FALSE,FALSE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_qn_se=apply((",i,"_result[,-1])[,c(FALSE,TRUE,FALSE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_mn_se=apply((",i,"_result[,-1])[,c(FALSE,FALSE,TRUE,FALSE)],1,sd)/sqrt(n)")))
    eval(parse(text = paste0(i,"_result_vsn_se=apply((",i,"_result[,-1])[,c(FALSE,FALSE,FALSE,TRUE)],1,sd)/sqrt(n)")))
    
    eval(parse(text = paste0("error = c(error,",i,"_result_non,",i,"_result_qn,",i,"_result_mn,",i,"_result_vsn)")))
    eval(parse(text = paste0("se = c(se,",i,"_result_non_se,",i,"_result_qn_se,",i,"_result_mn_se,",i,"_result_vsn_se)")))
  }
  result_2 = data.frame(error = error,
                             se = se,
                             ml = rep(ml,each=4*length(split_comination)),
                             norm = rep(c("None","QN","MN","VSN"),each=length(split_comination),length(ml)),
                             x=rep(1:length(split_comination),4*length(ml)))
  
  result <- rbind(result_1,result_2)
  p=ggplot(result,aes(x=x,y=error,color=ml,linetype=norm))+
    geom_line()+
    scale_x_continuous(breaks=1:(length(split_comination)+1),labels=c(paste("contrast 1 (", split_comination,")", sep = ""),"contrast 2 (100)"))+
    geom_errorbar(aes(ymin=error-se*1.96,ymax=error+se*1.96),width=0.1)+
    labs(x = "", title = paste(file_contrast1,"VS",file_contrast2))
  print(p)
}
```
